Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2015-03-19 draft.tex
acknowledge c2pap

We thank Ulrik Egede for insightful discussions and helpful comments on the
manuscript. We are grateful to Gudrun Hiller, Martin Jung and Konstantinos Petridis for helpful discussions,
as well as Claus Grupen for helpful advice in searching the literature.
The work of D.v.D has been supported by the Bundesministerium f\"ur Bildung und Forschung (BMBF).

>>>>

We thank Ulrik Egede for insightful discussions and helpful comments
on the manuscript. We are grateful to Gudrun Hiller, Martin Jung, and
Konstantinos Petridis for helpful discussions, as well as Claus Grupen
for helpful advice in searching the literature.  The work of D.v.D has
been supported by the Bundesministerium f\"ur Bildung und Forschung
(BMBF). F.B. is grateful for the support by the DFG Cluster of
Excellence "Origin and Structure of the Universe". Part of the
numerical simulations have been carried out on the computing
facilities of the Computational Center for Particle and Astrophysics
(C2PAP).
